---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# EXR

<!-- badges: start -->
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![R-CMD-check](https://github.com/obsaditelnost/EXR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/obsaditelnost/EXR/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/obsaditelnost/EXR/graph/badge.svg)](https://app.codecov.io/gh/obsaditelnost/EXR)
[![License: MIT](https://img.shields.io/badge/license-MIT-blue.svg)](https://cran.r-project.org/web/licenses/MIT)
<!-- badges: end -->

Get currency exchange rates ('EXR') or directly apply currency 
    conversion on a tibble from one to another currency based on spot prices 
    (avg) provided by 'ECB Data Portal'. If neither currency nor currency 
    denominator is EUR, unofficial cross-rates based on EUR will be calculated. 
    The main purpose of this package is to offer an unlimited and free way to
    get (potentially approximate) important exchange rates. No API-key required. 
    Data can be requested by periods with days as shortest period. No ask, bid,
    mid or intra-day data.

## Installation

You can install the development version of EXR from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("obsaditelnost/EXR")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(EXR)
# get firsr 10 rows of USD/EUR exchange rates for the last year,
# fill missing dates and look for missing values up to 3 days in the past
# so there won't be exchange rates on very long weekends that include holidays
EXR::get_exchange_rate_history(
 base_currency = "EUR",
 price_currency = "USD",
 periodicity = "D",
 fill_missing_dates = TRUE,
 max_lookback_days = 3
)[1:10, ]
```
